Backpropagating Gravitational wave events

### 2022-04-14 src/ms.tex
Commit before reworking

As the rate of detection of gravitational-wave (GW) increase with the sensitivity of the GW detector network \kw{},
understanding astrophysical processes related to progenitors of GW events through analyzing a population of GW events has become more popular \kw{cite}.
A very common way to study the origin of detected GW events is through population synthesis simulation \kw{cite},
which evolves a population of binaries to form a population of GW events.
Forward modelling of a population of GW events start with sampling a set of initial binary parameters from some distributions related to the progenitor population,
such as the initial mass function or star-formation history,
then evolve each individual members according to the physics of interest until some stopping criteria is met.
This usually mean either a merger event or the binary system stays stable for a Hubble time.
After this, one can collect all the GW emitting GW events in the synthetic population and compare to the observed population.

While forward modelling has been the canonical pathway to simulate binary systems and compare to GW observation,
it is not necessarily the most efficient way to constrain the underlying physical model.
Most of the systems do not end in a merger, and the systems ending up as merger events do not necessarily agree with the observation.
This means if we want to evolve a binary to match the observation by pure trial and error, a large fraction of computation will be wasted in trying initial binary configurations that are not related to the observation.
To alleviate this inefficiency, the community often takes a population approach --- instead of trying to match binary systems to observations event by event,
one can draw systems from an initial population, forward model each member in that population then match it to the observed population properties.
However, this approach is essentially trading one inefficiency with another, since we still need to choose an initial distribution of binary parameters.
For relatively well-known source properties such as initial masses this is less of a problem,
but the distribution of some less well-studied properties such as common envelope efficiency is often heuristically chosen to be some simple distribution such as a delta function at some value, i.e. a fixed value for the entire population.
This is a problem when the target of a study is to understand these less studied parameters, since one either need to justify their choice of distribution with other independent studies,
or they should vary the family of distributions.
In general, it is unclear how one can cover all possible distribution that may agree with the observation in generating a suite of simulations.
The problem worsen as we increase the dimensionality of the parameter space.
\wf{This says what you want to say, but it's a bit wordy right now---I'll return to it, but it would be good to tighten up the language a lot.}

>>>>

As the rate of detection of gravitational-wave (GW) increase with the sensitivity of the GW detector network \kw{},
understanding astrophysical processes related to progenitors of GW events through analyzing a population of GW events has become more popular \kw{cite}.
A very common way to study the origin of detected GW events is through population synthesis simulation \kw{cite},
which evolves a population of binaries to form a population of GW events.
Forward modelling of a population of GW events start with sampling a set of initial binary parameters from some distributions related to the progenitor population,
such as the initial mass function or star-formation history,
then evolve each individual members according to the physics of interest until some stopping criteria is met.
This usually mean either a merger event or the binary system stays stable for a Hubble time.
After this, one can collect all the GW emitting binaries in the synthetic population and compare to the observed population.

\kw{Shorten}
While forward modelling has been the canonical pathway to simulate binary systems and compare to GW observation,
it is not necessarily the most efficient way to constrain the underlying physical model.
Most of the systems do not end in a merger, and the systems ending up as merger events do not necessarily agree with the observation.
This means if we want to evolve a binary to match the observation by pure trial and error, a large fraction of computation will be wasted in trying initial binary configurations that are not related to the observation.
To alleviate this inefficiency, the community often takes a population approach --- instead of trying to match binary systems to observations event by event,
one can draw systems from an initial population, forward model each member in that population then match it to the observed population properties.
However, this approach is essentially trading one inefficiency with another, since we still need to choose an initial distribution of binary parameters.
For relatively well-known source properties such as initial masses this is less of a problem,
but the distribution of some less well-studied properties such as common envelope efficiency is often heuristically chosen to be some simple distribution such as a delta function at some value, i.e. a fixed value for the entire population.
This is a problem when the target of a study is to understand these less studied parameters, since one either need to justify their choice of distribution with other independent studies,
or they should vary the family of distributions.
In general, it is unclear how one can cover all possible distribution that may agree with the observation in generating a suite of simulations.
The problem worsen as we increase the dimensionality of the parameter space.
\wf{This says what you want to say, but it's a bit wordy right now---I'll return to it, but it would be good to tighten up the language a lot.}
